---
title: "p8105_hw6_qh2284"
author: "Qin Huang"
date: "2023-11-17"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(ggplot2)
```

## Problem 1

```{r}
# load the dataset
homi = read_csv("./dataset/homicide-data.csv")
```

**Create a `city_state` variable (e.g. \"Baltimore, MD\"), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO -- these don\'t report victim race. Also omit Tulsa, AL -- this is a data entry mistake. For this problem, limit your analysis those for whom `victim_race` is `white` or `black`. Be sure that `victim_age` is numeric.**

```{r}
homi <- homi %>% 
  mutate(city_state = paste0(city,", ",state),
    solved = ifelse(disposition == "Closed by arrest",1,0)) %>% 
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>%
  filter(victim_race == "White" | victim_race == "Black") %>% 
  mutate(victim_age = as.numeric(victim_age))
```

**For the city of Baltimore, MD, use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of `glm` as an R object; apply the `broom::tidy` to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.**

```{r}
balt = homi %>% 
  filter(city == "Baltimore") %>% 
  select(solved, victim_age, victim_race, victim_sex) %>%
  mutate(victim_sex = fct_relevel(victim_sex, "Female"))
```

```{r}
balt_model = balt %>% 
  glm(solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())
```

```{r}
# save R object
save(balt_model, file = "./result/Baltimore_logistic_model.RData")
```

```{r}
balt_model %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

```{r}
odd_ci_balt = balt_model %>% 
  broom::tidy() %>%
  filter(term == 'victim_sexMale') %>% 
  summarise(estimate = estimate,
            OR = exp(estimate),
         OR_lower = exp(estimate - 1.96 * std.error),
         OR_upper = exp(estimate + 1.96 * std.error) ) %>%
  knitr::kable(digits = 3)

odd_ci_balt
```

**Now run `glm` for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a \"tidy\" pipeline, making use of `purrr::map`, list columns, and `unnest` as necessary to create a dataframe with estimated ORs and CIs for each city.**

```{r}
# create a function
all_model = function(citystate){
  city_glm = homi %>% 
    filter(city_state == citystate) %>% 
    glm(solved ~ victim_sex + victim_race + victim_age, family = binomial, data = .) %>% 
    broom::tidy() %>% 
    filter(term == "victim_sexMale") %>% 
    summarise(
         estimate = estimate,
         OR = exp(estimate), 
         OR_lower = exp(estimate - 1.96*std.error), 
         OR_upper = exp(estimate + 1.96*std.error))
    
    city_glm
}
```

```{r}
glm_all = homi %>%
  dplyr::select(city_state) %>%
  unique() %>%
  mutate(glm = map(city_state, all_model)) %>% 
  unnest(glm) %>% 
  arrange(desc(OR))

glm_all %>%
  knitr::kable(digits = 3)
```

**Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.**

```{r}
ggplot(glm_all, aes(x=OR, y = fct_reorder(city_state, OR))) +
  geom_point() +
  geom_errorbar(aes(xmin = OR_lower, xmax = OR_upper)) +
  labs(x = 'OR with 95% CI', y = 'city_state', title = 'Estimated ORs and CIs for each city') +
  theme(axis.text.y = element_text(hjust = 1,size = 6))
```
